Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-12 paper/main.tex
Intro comment

% hypo a
We hypothesize[d] that whole-brain analyses will/would reveal increased
hemodynamic activity spatially constrained \todo{i.e. not activity all over the
place} to the PPA as functionally defined by a visual localizer experiment using
pictures done with the same subjects.  \citep{sengupta2016extension}.
% hypo b
Focussing on the [``cleaner operationalization'' of the] audio-description, we
further hypothesize[d] that an exclusively auditory stimulus can/could
substitute a block-design experiment using pictures to localize a ``visual
area'' in individual subjects.
% results: group
On a group average level,
% operationalization in naturalistic stimuli
results demonstrate that our approach based on annotations [of two ecologically
more valid stimuli] to operationalize spatial perception lead to increased
hemodynamic activity in [roughly] the same brain regions the block-designed
visual localizer.\todo{interpretation?}
% anterior vs. posterior
On both a group and individual subject level, a comparison of results from the
three datasets also suggests functional differences between the anterior and
posterior PPA.
% what does it mean
The current data add evidence to the hypothesis that the PPA might consist of
submodules that work together during visual perception of landscapes (cf.
\citep{baldassano2013differential}).
%
Lastly, our results suggest that the PPA's anterior part can be localized in
individual subjects by contrasting high-level semantic information occurring in
an auditory naturalistic stimulus.

>>>>

% hypo a
We hypothesize[d] that whole-brain analyses will/would reveal increased
hemodynamic activity spatially constrained \todo{i.e. not activity all over the
place} to the PPA as functionally defined by a visual localizer experiment using
pictures done with the same subjects.  \citep{sengupta2016extension}.
% hypo b
Focussing on the [``cleaner operationalization'' of the] audio-description, we
further hypothesize[d] that an exclusively auditory stimulus can/could
substitute a block-design experiment using pictures to localize a ``visual
area'' in individual subjects.\todo{needs short statement on why one would even want that}
% results: group
On a group average level,
% operationalization in naturalistic stimuli
results demonstrate that our approach based on annotations [of two ecologically
more valid stimuli] to operationalize spatial perception lead to increased
hemodynamic activity in [roughly] the same brain regions the block-designed
visual localizer.\todo{interpretation?}
% anterior vs. posterior
On both a group and individual subject level, a comparison of results from the
three datasets also suggests functional differences between the anterior and
posterior PPA.
% what does it mean
The current data add evidence to the hypothesis that the PPA might consist of
submodules that work together during visual perception of landscapes (cf.
\citep{baldassano2013differential}).
%
Lastly, our results suggest that the PPA's anterior part can be localized in
individual subjects by contrasting high-level semantic information occurring in
an auditory naturalistic stimulus.
